---
title: "customFunctions"
author: "Yordan García Corrales"
date: "24/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Get a dataframe
```{r}
mean_min<- function(datas){
  mean<- mean(datas)
  min<-min(datas)
  
  return(data.frame(Mean=mean,Min=min))
}

mean_min(seq(1:6))
```

#Get th greatest
```{r}
greatest<-function(num1,num2){
  result<-NULL
  if(num1==num2){
    result<-paste0("Iquals")
  }else if(num1>num2){
    result<-paste0("The greatest is num1 ",num1)
  }else{
    result<-paste0("The greatest is num2 ",num2)
  }
  return(result)
}

greatest(23,23)
greatest(23,14)
greatest(23,41)
```

#Sum number > 0
```{r}

sumGreater0<-function(numbers){
  total<-sum(numbers[numbers>0])
  return(total)
}

sumGreater0(sample(-5:5))
```

#Sum number < 0 but in positive
```{r}
sumLower0<-function(numbers){
  total<-abs(sum(numbers[numbers<0]))
  return(total)
}

sumLower0(sample(-5:5))
```

#Count how many numbers are greater than 0
```{r}
countGreater0<-function(numbers){
  amount<-length(numbers[numbers>0])
  return(amount)
}
numbers1<-sample(-10:10,10);sort(numbers1)
countGreater0(numbers1)
numbers2<-sample(-5:5,10);sort(numbers1)
countGreater0(numbers2)
```


```{r}
factor.count<-function(element){
  if(is.factor(element)==TRUE){
    table(element)
  }else{
    cat("Element is not a factor")
  }
}

marital.status <- factor(x=c("married","single","widower","divorced","married","single"),levels=c("married","single","widower","divorced"))
marital.status

factor.count(marital.status)
factor.count(c(1:3))
```

#Method that calculate a good health
```{r}

#Gender=1 Male, Gender=0 Female
TMBHM <- function(kilog,height,age, gender=0){
  
  #Lista de ponderadores
  p01 <- ifelse(gender==1,66.4730,655.0955) 
  p02 <- ifelse(gender==1,13.7516,9.5634)
  p03 <- ifelse(gender==1,5.0033,1.8449) 
  p04 <- ifelse(gender==1,6.7550,4.6756) 

  resultado <- round(p01 +(p02 * kilog) + (p03 * height) - (p04* age),0)
  
  return(resultado)
}

TMBHM(110,180,32,1)
TMBHM(80,163,32)
```

#Method that calculate a good health + change
```{r}
#Gender=1 Male, Gender=0 Female
#c =contexture 1=normal,Muscular 2, Overweight 0
TMBHMC <- function(kilog,height,age, gender=1, c=2){
  
  #Lista de ponderadores
  p01 <- ifelse(gender==1,66.4730,655.0955) 
  p02 <- ifelse(gender==1,13.7516,9.5634)
  p03 <- ifelse(gender==1,5.0033,1.8449) 
  p04 <- ifelse(gender==1,6.7550,4.6756) 

  result <- round(p01 +(p02 * kilog) + (p03 * height) - (p04* age),0)
  
  
  if(c==0){
    finalResult<-result*0.85
  }else if(c==1){
    finalResult<-result*1.10
  }else{
   finalResult<- result
  }
  return(round(finalResult,0))
}
TMBHMC(110,180,32,1,2)#Normal 2
TMBHMC(110,180,32,1,1)#Muscular 1
TMBHMC(110,180,32,1,0)#Overweight 0


TMBHMC(110,180,32,0,2)#Normal 2
TMBHMC(110,180,32,0,1)#Muscular 1
TMBHMC(110,180,32,0,0)#Overweight 0

```

#Contribution to the variation rate
```{r}
contribution <- function(v1,v2){
  
  partic <- v1/sum(v1)
  variac <- (v2-v1)/v1*100
  ap_F <- partic*variac
  sums <- c(sum(v1),sum(v2),sum(partic),((sum(v2)-sum(v1))/sum(v1))*100,sum(ap_F))
  
  tabla <- data.frame(A_Base=round(v1,2),A_Interest=round(v2,2),Part.=round(partic,2),
                        Tasa.var=round(variac,2),Input=round(ap_F,2))
  
  R <- rbind(tabla,round(sums,2))
  
  return(R)
  
}

ve1 <- sample(1:30,5)
ve2 <- sample(1:30,5)

Datas03 <- contribution(ve1,ve2)
Datas03
```

#Read from xlsx
```{r}
prices<- readxl::read_xlsx("Precios.xlsx")
prices

Datas04 <- contribution(prices$Precio1,prices$Precio2)
Datas04

rownames(Datas04)<- c(prices$Descripcion_Producto,"Total")
Datas04
```

#Normalization through the point of correspondence.
```{r}
correspondence <- function(element,array){#Execute each element in array
  
  result <- round((element-min(array))/(max(array)-min(array))*100,2)
  
  return(result)

}

array1 <- c(16,6,12,5,9,7,8,2,11,15)
array1
correspondence(array1,array1)
```

```{r}
array2 <- sample(1000:10000,10)
array2
correspondence(array2,array2)
```

#Confidence intervals knowing, unknown
```{r}
confidence_Intervals_Knowing <- function(datas,c,st){ 
  # datas 
  # c= Statistic value z
  # st= Standard Desviation.
        
      Data_inf <- mean(datas)-c*(st/sqrt(length(datas)))
      Data_sup <- mean(datas)+c*( st/sqrt(length(datas)))        
      
  return(data.frame(Inferior_Limit=round(Data_inf,2),Sup_Limit=round(Data_sup,2)))}

confidence_Intervals_Unknown <- function(datas,c){
  
      Data_inf <- mean(datas)-c*(sd(datas)/sqrt(length(datas)))
      Data_sup <- mean(datas)+c*(sd(datas)/sqrt(length(datas))) 
  
  return(data.frame(Inferior_Limit=round(Data_inf,2),Sup_Limit=round(Data_sup,2)))}
```

#Examples
```{r}
Prices_1 <- sample(100:300,100,replace = T)
Prices_1

confidence_Intervals_Knowing(Prices_1,1.96,4) 
```

```{r}
confidence_Intervals_Unknown(Prices_1,1.96) 
```

