---
title: "Regular expressions"
author: "Yordan García Corrales"
date: "18/6/2020"
output: 
  html_document:
     toc: true
     toc_depth: 6
     number_section: true
     toc_float: true
     theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressWarnings(suppressMessages(library(stringr)))
suppressWarnings(suppressMessages(library(DT)))
suppressWarnings(suppressMessages(library(lubridate)))
```
# Regular Expressions
```{r}
text01 <- "The salary is $2000 and per year $24000 is not the same as 2000^2 then it is 4000000 millions"

text02 <- "Please write to cisprocr.sa@gmail.com for more information"

text01; text02
```
## Find a specific word
```{r}
str_view_all(string = text01, pattern ="2000" )
str_view_all(string = text01, pattern ="\\$2000" )#To get a symbol that is from R
```

```{r}
str_view_all(string = text01,pattern = "[0-9]")#All numbers
str_view_all(string = text01,pattern = "[0-9]+")#All numbers together
str_view_all(string = text01,pattern = "\\w")#Split letter by letter
str_view_all(string = text01,pattern = "\\w+")#Split word by word
str_view_all(string = text01,pattern = "\\W")#Get all that is not a letter
str_view_all(string = text01,pattern = "\\W+")#Get all that is not a letter + symbols
```

### Get word with an specific pattern
```{r}
str_view_all(string = text01,pattern = "(?<=\\$)[0-9]+") #Get all number after $
str_view_all(string = text01,pattern = "(?<=\\s)[0-9]+") #Get all number after space
str_view_all(string = text01,pattern = "[0-9]+(?=\\s)")#Get all number before and space
str_view_all(string = text01,pattern = "\\$[0-9]+(?=\\s)")#Get all number before and space + that has an $
```

## Get text 
```{r}
str_extract_all(string = text01,pattern = "2000") #Get all 2000
numbersList<-str_extract_all(string = text01,pattern = "[0-9]+")#Get all numbers
numbersList
str_extract_all(string = text01,pattern = "(?<=\\$)[0-9]+")#Get numbers that begin wih $
str_extract_all(string = text01,pattern = "\\$[0-9]+(?=\\s)")#Get all numbers that finish with an space and start with  $ 

#Just to know this function return a List
mode(numbersList)
```

### Change a str to number
```{r}
numericList<-as.numeric(numbersList[[1]])
numericList
sum(numericList)
```
## Change parts in a text
```{r}
provinces <- c("San José", "Alajuela", "Cartago",
                "Heredia", "Guanacaste","Puntarenas",
                "Limón")

provinces
```

```{r}
#Replace spaces
str_replace_all(string = provinces,pattern = "[:space:]",replacement = "_")

#Replace to NA when a word has an i
listNA<-str_replace_all(string = provinces, pattern = "i", replacement = NA_character_)
listNA
```
### Delete all NA characters
```{r}
is.na(listNA) #Logic values
newList<-listNA[!is.na(listNA)]
newList
```

### Replace word by word using gsub

```{r}
text01
gsub(pattern = "salary",replacement = "gain", x = text01)

```

```{r}
text01
gsub(pattern = "is",replacement = "-", x = text01)
```

```{r}
text01
gsub(pattern = "\\$",replacement = "USD", x = text01)
```

## Creating text with space o without.
```{r}
paste("Word1","Word2")#The function add a space between each word.
paste("Word1","Word2",sep = "")#Sep without space
paste0("Word1","Word2")#Without space
paste0("Date_",today())
```

## Function examples
```{r}
spaces <- function(v){

  library(stringr) #Install
  
  # Delete spaces by position
  un_esp <- str_replace_all(v, pattern="[:space:]+",replacement=" ")
  
  # Detele spaces at start and at the end.
  result <- str_trim(un_esp, side = "both")
  
  return(result)
}

text06 <- c("Monday and Tuesday  ", 
            "   Monday and Tuesday   ",
            "   Monday    and   Tuesday   ")
text06

spaces(text06)
```
### Upper,lower, title
```{r}
text01
str_to_upper(text01)
str_to_lower(text01)
str_to_title(text01)
```
#### Duplicate
```{r}
fruit <- c("apple", "pear", "banana")

str_dup(fruit,2)
str_dup(fruit,1:3)
str_c("ba", str_dup("na", 0:5))
```

### Count letters
```{r}
fruit <- c("apple", "banana", "pear", "pineapple")

str_count(fruit, "a")
```

### Remove vowels
```{r}
fruits <- c("one apple", "two pears", "three bananas")

str_remove(fruits, "[aeiou]")# Remove one by place in fruits
str_remove_all(fruits, "[aeiou]") 
```
### Creating logic arrays
```{r}
fruit <- c("apple", "banana", "orange", "pinapple")

str_starts(fruit, "p") #True = starts with p
str_starts(fruit, "p", negate = TRUE)#True != starts with p
```

```{r}
str_ends(fruit, "e") #True = ends with e
str_starts(fruit, "e", negate = TRUE)#True != starts with p
```
### General examples

```{r}
str_c("Letter", letters, sep = ": ")
```

```{r}
str_c(letters, " is for", "...")
str_c(letters, collapse = "")
```
## Stringr
### All numbers have to have this format 888-888-8888
```{r}
strings <- c(" 219 733 8965", "329-293-8753 ", "banana", "595 794 7569",
"387 287 6718", "apple", "233.398.9187 ", "482 952 3315",
"239 923 8115 and 842 566 4692", "Work: 579-499-7527", "$1000",
"Home: 543.355.3679")

strings

phonePattern<- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"

phones<-str_extract(string =strings, pattern = phonePattern)
phones

phones<-phones[!is.na(phones)]
phones

formatPhones<-str_replace_all(phones,pattern = "[:space:]",replacement = "-")
formatPhones
# Use \\. because delete all elements. "." is reserved
formatPhonesFinal<-gsub(formatPhones,pattern = "\\.",replacement = "-")
formatPhonesFinal
```
#### Save in a data frame.

```{r}
Datas<- data.frame(Client=str_c("Client",1:9,sep = ": "),formatPhonesFinal)
Datas
```

### Creating a function

```{r}
Tel_USA<-function(numbers){
  library(stringr)
  
  phonePattern<- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"

  phones<-str_extract(string =numbers, pattern = phonePattern)
  phones<-phones[!is.na(phones)]
  
  phones<-str_replace_all(phones,pattern = "[:space:]",replacement = "-")
  phones<-gsub(phones,pattern = "\\.",replacement = "-")
  
  n<-length(phones)
  
  Datas<- data.frame(Client=str_c("Client",1:n,sep = ": "),phones)
  return(Datas)
}

strings <- c(" 219 733 8965", "329-293-8753 ", "banana", "595 794 7569",
"387 287 6718", "apple", "233.398.9187 ", "482 952 3315",
"239 923 8115 and 842 566 4692", "Work: 579-499-7527", "$1000",
"Home: 543.355.3679")

Tel_USA(strings)

strings2<-rep(strings,3)
Tel_USA(strings2)
```

