---
title: "DataBase 1"
author: "Yordan García Corrales"
date: "3/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(tidyr)))
suppressWarnings(suppressMessages(library(lubridate)))
suppressWarnings(suppressMessages(library(DT)))

Sys.setlocale(locale="es_ES.UTF-8") # para uso de los nombres de días y meses en español
```


# DataBase 1
## Creating a Database
```{r}
DB <- data.frame(read.csv2("BD1.csv"))
datatable(head(DB))
```
## Types in database
```{r}
str(DB)
```

### Transform datas
```{r}
DB$Fecha <- dmy(DB$Fecha) #Now Fecha is Date
datatable(head(DB))
```

```{r}
str(DB)
```

## Add new datas
```{r}
# Add Selss
DB1 <- DB %>% mutate(Sells=Cantidad*Precio.Unitario)

# Add Minutes
DB2 <- DB1 %>% mutate(Minutos=round(Horas_en_venta*60,0))

# Add week's day
DB3 <- DB2 %>% mutate(Dia=wday(Fecha,label = T,abbr = F))

# Add group of week
DB4 <- DB3 %>% mutate(Group_Days=ifelse(Dia=="sábado" | Dia=="domingo",
                                      "weekend", "weekday"))
datatable(head(DB4))
```
## Example 1
#Know if the seller sells in a different place
```{r}
DB4<-DB4 %>% mutate(kindplace=ifelse(Residencia==Ruta,"Internal","External"))
DB4
```

#If it is external you have to add the 0.5% of Sells to the seller
```{r}
DB5<- DB4 %>% mutate(AmountReco=round(ifelse(kindplace=="External",Sells*0.005,0)))
DB5
```
## Example 2
#Calculate the total to pay for each employee
```{r}
#Calcula the procentaje
DB6<-DB5 %>% mutate(ProcenComision=as.double(ifelse(Group_Days=="weekend" & kindplace=="External",0.025,
                                     ifelse(Group_Days=="weekday" & kindplace=="External",0.02,
                                            ifelse(Group_Days=="weekday" & kindplace=="Interal",0.015,0.01)))))
DB6
```

```{r}
DB7 <- DB6 %>% mutate(AmountByComision=Sells*ProcenComision)
DB8 <- DB7 %>% mutate(TotalPay=AmountByComision+AmountReco)
DB8
```
#New columns
```{r}
DB9 <- DB8 %>% mutate(Rentab_min=round(Sells/Minutos,2)) 

head(DB9)
```

```{r}
DB10 <- DB9 %>% mutate(Part_PT=round(TotalPay/sum(TotalPay),4)*100) 

head(DB10)
```

```{r}
DB11 <- DB10 %>% mutate(Start_Selling=Edad-Años_Experiencia)

head(DB11)

#Experience
range(DB11$Años_Experiencia)
```

```{r}
DB12 <- DB11 %>% mutate(Rango_Exp=
                ifelse(Años_Experiencia %in% 1:4,"less than 5",
                ifelse(Años_Experiencia %in% 5:10,"between 5 and 10",
                ifelse(Años_Experiencia %in% 11:20,"between 11 and 20",
                ifelse(Años_Experiencia %in% 21:30,"between 21 and 30","more than 30 years")))))

head(DB12)
```

#Range of sellings
```{r}
range(DB12$Sells)
```
#Categority by type of employee
```{r}
DB14 <- DB12 %>% mutate(Type_Seller=
                ifelse(Sells %in% 1:1000,"New",
                ifelse(Sells %in% 1001:300000,"Average",
                ifelse(Sells %in% 300001:600000,"Good",
                "Excelent"))))

head(DB14)
```

#Sumarize
```{r}
R01 <- DB14 %>% group_by(Type_Seller) %>% count(Type_Seller)
R01
```

#Sumarize by product
```{r}
R02 <- DB14 %>% group_by(Producto) %>% summarise(prom=round(mean(Sells),2))
R02
```
#Datas from begining database
```{r}
v01<-names(DB)

v01
```
#Datas from last database
```{r}
v02<-names(DB14)
v02
```

